Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

We observe significant dWER increasing without concatenating the reference audio to the mixture, 
as shown 
the TSELM-S-NoConcat in Table \ref{main_exp}. WavLM \cite{wavlm} is demonstrated to have target speaker 
separation capability. The input audio should have the mixture less than 50\% and have the first utterance as target speaker. The output will be a coarse denoised audio emphasizing the target speaker. 
If the whole input is mixture, we have found that WavLM sometimes will 
extract the wrong speaker. Our current pipeline focuses on the separation strategy

>>>>

We observe significant dWER increasing without concatenating the reference audio to the mixture, 
as shown 
the TSELM-S-NoConcat in Table \ref{main_exp}. WavLM \cite{wavlm} is demonstrated to have target speaker 
separation capability. The input audio should have the mixture less than 50\% and have the first utterance as target speaker. The output will be a coarse denoised embedding emphasizing the target speaker. 
If the whole input is mixture, we have found that WavLM sometimes will 
extract the wrong speaker. Inspired by SELM's \cite{selm} success in speech denoising. Our pipeline is trying to transform
the target speaker separation problem to speech enhancement problem by using WavLM's denoising capability.
